|

### 2021-02-23 appendix/appendix.Rmd
small edits to appendix, gitignore

\begin{figure}
\centering
\includegraphics[width=0.8\textwidth]{../figures/rvWorkBlock.png}
\caption{Example Leaflet.\label{appcevwbl}}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics[width=0.8\textwidth]{../figures/rvWorkArea.png}
\caption{Example Working Area.\label{appcevwa}}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics[width=0.8\textwidth]{../figures/rvKit3.jpeg}
\caption{Teams Uniforms\label{appcteamunif}}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics[width=0.4\textwidth]{../figures/rvApp.jpeg}
\caption{Cellphone with Data Collection App.\label{appccpdcit}}
\end{figure}

@@

\begin{figure}
\includegraphics[width=0.8\textwidth]{../figures/rvKit4.jpg}
\includegraphics[width=0.8\textwidth]{../figures/rvKit5.jpg}
\caption{Example Leaflet Handed to Households.\label{appcexhhleafl}}
\end{figure}

@@

## Some field pictures

@@

\begin{figure}
\centering
\includegraphics[width=0.7\textwidth]{../figures/rvFieldPic1.png}
\caption{Field pictures}
\end{figure}

\begin{figure}
\centering
\includegraphics[width=0.7\textwidth]{../figures/rvFieldPic2.jpg}
\caption{Field pictures}
\end{figure}

@@

```{r}
sessionInfo()
```

>>>>

\begin{figure}
\centering
\includegraphics[width=0.8\textwidth, height=13cm]{../figures/rvWorkBlock.png}
\caption{Example Leaflet.\label{appcevwbl}}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics[width=0.8\textwidth, height=11cm]{../figures/rvWorkArea.png}
\caption{Example Working Area.\label{appcevwa}}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics[width=0.8\textwidth, height=9cm]{../figures/rvKit3.jpeg}
\caption{Teams Uniforms\label{appcteamunif}}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics[width=0.4\textwidth, height=6cm]{../figures/rvApp.jpeg}
\caption{Cellphone with Data Collection App.\label{appccpdcit}}
\end{figure}

@@

\begin{figure}
\includegraphics[width=0.8\textwidth, height=7cm]{../figures/rvKit4.jpg}
\includegraphics[width=0.8\textwidth, height=7cm]{../figures/rvKit5.jpg}
\caption{Example Leaflet Handed to Households.\label{appcexhhleafl}}
\end{figure}

@@

## Some Field Pictures

@@

\begin{figure}
\centering
\includegraphics[width=0.7\textwidth, height=12cm]{../figures/rvFieldPic1.png}
\caption{Field pictures}
\end{figure}

\begin{figure}
\centering
\includegraphics[width=0.7\textwidth, height=10cm]{../figures/rvFieldPic2.jpg}
\caption{Field pictures}
\end{figure}

@@

\footnotesize
```{r}
sessionInfo()
```
\normalsize
